Hydra Battles and Cie

### 2021-05-10 doc/hydras.tex
consistent use of capitalization in headers
work on coqdoc comments
chantier
corrections of typos

\documentclass[a4paper]{book}
\usepackage{alltt}
\usepackage{multind}
\usepackage{hyperref}
\usepackage{url}
\usepackage{mdframed}
\usepackage{amsmath}
\usepackage{varioref}
\usepackage{synttree, proof, centernot}
\usepackage[firstpage]{draftwatermark}
\usepackage{verbatim}
\usepackage[note]{marginote}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{float}
\usepackage{threeparttable}
\setcounter{tocdepth}{1}
\input{coqmacros}

@@

It may also happen that some proof looks to be useless, because the proven theorem is a trivial consequence of another (proven too) result.
For instance, let us consider the three following statements:
\begin{enumerate}
\item There is no measure into $\mathbb{N}$ for proving the termination of all hydra battles (Sect~\vref{omega-case}).
\item There is no measure into the interval\footnote{We use the notation $[a,b)$ for denoting the set of ordinals greater or equal than $a$ and strictly less than $b$.} interval $\{x\$[0,\omega^2)$ for proving the termination of all hydra battles (Sect~\vref{omega2-case}).
\item There is no measure into $[0,\mu)$ for proving the termination of all hydra battles, for any $\mu<\epsilon_0$ (Sect\vref{sec:free-battles-case}).
\end{enumerate}

@@

\subsection{Alternative or bad definitions}
\label{sect:alt-proofs}
Finally, we decided to include definitions or lemma statements, as well as tactics,  that lead to
dead-ends or too complex developments, with the following coloring.
Bad definitions 
 and encapsulation in modules called \texttt{Bad}, \texttt{Bad1}, etc.

@@

\part{Hydras and Ordinals}

\include{part-hydras}
\include{chapter-primrec}
\part{A Few  Certified Algorithms}

>>>>

\documentclass[a4paper]{book}
\usepackage{alltt}
\usepackage{multind}
\usepackage{hyperref}
\usepackage{url}
\usepackage{xcolor,fancyvrb, mdframed}
\usepackage{amsmath}
\usepackage{varioref}
\usepackage{synttree, proof, centernot}
\usepackage[firstpage]{draftwatermark}
\usepackage{verbatim}
\usepackage[note]{marginote}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{float}
\usepackage{threeparttable}
\usepackage{fontspec}
\usepackage{mathtools}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{placeins}
\usepackage{tikz}
\usepackage{tikzsymbols}
\usetikzlibrary{arrows}
\usepackage{graphicx}
\usepackage{amsmath,mathdots,dsfont}
\usepackage{amssymb}
\usepackage{newunicodechar}
\usepackage{theorem}

\setcounter{tocdepth}{1}
\input{coqmacros}

@@

It may also happen that some proof looks to be useless, because the proven theorem is a trivial consequence of another (proven too) result.
For instance, let us consider the three following statements:
\begin{enumerate}
\item There is no measure into $\mathbb{N}$ for proving the termination of all hydra battles (Sect~\vref{omega-case}).
\item There is no measure into the interval\footnote{We use the notation $[a,b)$ for denoting the set of ordinals greater or equal than $a$ and strictly less than $b$.}  $[0,\omega^2)$ for proving the termination of all hydra battles (Sect.~\vref{omega2-case}).
\item There is no measure into $[0,\mu)$ for proving the termination of all hydra battles, for any $\mu<\epsilon_0$ (Sect.\vref{sec:free-battles-case}).
\end{enumerate}

@@

\subsection{Alternative or bad definitions}
\label{sect:alt-proofs}
Finally, we decided to include definitions or lemma statements, as well as tactics,  that lead to
dead-ends or too complex developments, with the following coloring.
Bad definitions 
 are ''masked '' inside modules called \texttt{Bad}, \texttt{Bad1}, etc.

@@

\part{Hydras and ordinals}

\include{part-hydras}
\include{chapter-primrec}
\part{A few  certified algorithms}

### 2021-05-10 doc/part-hydras.tex
minor corrections
small changes
correction of typos
chantier
corrections of typos

\item We prove a relation between the length of a ``classic''  class of  battles \footnote{This class is also called \emph{standard} in this document (text and proofs). The \emph{replication factor} of the hydra is exactly $i$ at the $i$-th round of the battle (see Sect~\vref{sect:replication-def}).}
and the Wainer-Hardy hierarchy of ``rapidly growing functions'' $H_\alpha$~\cite{Wainer1970}. The considered class of battles, which we call \emph{standard}  is the most considered one in the scientific  litterature(including popularization).
\end{itemize}

@@

The following function ``gnaws'' an ordinal $\alpha$, folowing a sequence of indices (ignoring the $0$s).
\noindent
\emph{From Module~\href{../theories/html/hydras.Epsilon0.Paths.html\#gnaw}{Epsilon0.Paths}}

@@

{\Large
$$
H_{\omega^3}(3) =  2 ^ {(2 ^ {N + 1} \times (N+1) } )  \times  (2 ^ {N+1} \times ( N +1) ) - 1
$$
}

@@

\section{The wainer hierarchy (functions \texorpdfstring{$F_\alpha$}{F\_alpha})}
\label{sect:wainer}

>>>>

\item We prove a relation between the length of a ``classic''  kind of  battles \footnote{This class is also called \emph{standard} in this document (text and proofs). The \emph{replication factor} of the hydra is exactly $i$ at the $i$-th round of the battle (see Sect~\vref{sect:replication-def}).}
and the Wainer-Hardy hierarchy of ``rapidly growing functions'' $H_\alpha$~\cite{Wainer1970}. The considered class of battles, which we call \emph{standard}  is the most considered one in the scientific  litterature(including popularization).
\end{itemize}

@@

The following function ``gnaws'' an ordinal $\alpha$, following a sequence of indices (ignoring the $0$s).
\noindent
\emph{From Module~\href{../theories/html/hydras.Epsilon0.Paths.html\#gnaw}{Epsilon0.Paths}}

@@

{\Large
$$
H_{\omega^3}(3) =  2 ^ {(2 ^ {N + 1} \, (N+1) )}   \,  (2 ^ {N+1} \, ( N +1) ) - 1
$$
}

@@

\section{The Wainer hierarchy (functions \texorpdfstring{$F_\alpha$}{F\_alpha})}
\label{sect:wainer}
